Modeling Univariate and Multivariate Stochastic Volatility in \proglang{R} with \stochvol{} and \factorstochvol

### 2021-05-11 article.Rnw
decrease vignette size

@@

\graphicspath{{extrafig/}}

@@

<<setup, include=FALSE, cache=FALSE>>=
knitr::render_sweave()
knitr::opts_chunk$set(prompt = TRUE,
                      fig.show = "hide",
                      fig.keep = "high",
                      warning = FALSE,
                      error = FALSE,
                      message = FALSE,
                      echo = FALSE,
                      cache = FALSE,
                      fig.path = "Figures/jss2014-",
                      tidy = FALSE)
base::options(continue = "+  ", prompt = "R> ", width = 70,
  useFancyQuotes = FALSE)
plotevery <- 10L # can be used for trace plots to make vignette smaller
@

>>>>

\DeclareGraphicsExtensions{%
  .png,.PNG,%
  .pdf,.PDF,%
  .jpg,.mps,.jpeg,.jbig2,.jb2,.JPG,.JPEG,.JBIG2,.JB2}

@@

@@

<<setup, include=FALSE, cache=FALSE>>=
knitr::render_sweave()
knitr::opts_chunk$set(prompt = TRUE,
                      fig.show = "hide",
                      fig.keep = "high",
                      warning = FALSE,
                      error = FALSE,
                      dev = c("png", "pdf"),
                      dpi = 90,
                      message = FALSE,
                      echo = FALSE,
                      cache = TRUE,
                      fig.path = "Figures/jss2014-",
                      tidy = FALSE)
base::options(continue = "+  ", prompt = "R> ", width = 70,
  useFancyQuotes = FALSE)
plotevery <- 10L # can be used for trace plots to make vignette smaller
@

### 2021-05-11 article2.Rnw
decrease vignette size

<<setup, include=FALSE, cache=FALSE>>=
knitr::render_sweave()
knitr::opts_chunk$set(prompt = TRUE,
                      fig.show = "hide",
                      warning = FALSE,
                      error = FALSE,
                      message = FALSE,
                      echo = FALSE,
                      cache = FALSE,
                      fig.path = "Figures2/jss3813-",
                      tidy = FALSE)
base::options(continue = "+  ", prompt = "R> ", width = 70,
  useFancyQuotes = FALSE)

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{jss3813-svlplot-1.pdf}
  \caption{The default plot of an estimated model.
  The top row shows a summary of the posterior of the daily volatility (in percent) $100\exp(\bm h/2)$ through its median (black) and 5\% and 95\% quantiles (gray).
  The remaining panels summarize the Markov chains of the parameters $\mupar$, $\phipar$, $\sigmapar$, and $\rhopar$.
  In particular, the middle row presents trace plots and the bottom row shows prior (gray, dashed) and posterior (black, solid) densities.}
  \label{fig:svlall}
\end{figure}

>>>>

<<setup, include=FALSE, cache=FALSE>>=
knitr::render_sweave()
knitr::opts_chunk$set(prompt = TRUE,
                      fig.show = "hide",
                      warning = FALSE,
                      error = FALSE,
                      dev = c("pdf", "png"),
                      dpi = 90,
                      message = FALSE,
                      echo = FALSE,
                      cache = TRUE,
                      fig.path = "Figures2/jss3813-",
                      tidy = FALSE)
base::options(continue = "+  ", prompt = "R> ", width = 70,
  useFancyQuotes = FALSE)

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{jss3813-svlplot-1}
  \caption{The default plot of an estimated model.
  The top row shows a summary of the posterior of the daily volatility (in percent) $100\exp(\bm h/2)$ through its median (black) and 5\% and 95\% quantiles (gray).
  The remaining panels summarize the Markov chains of the parameters $\mupar$, $\phipar$, $\sigmapar$, and $\rhopar$.
  In particular, the middle row presents trace plots and the bottom row shows prior (gray, dashed) and posterior (black, solid) densities.}
  \label{fig:svlall}
\end{figure}
